---
title: "Energy AI"
author: "Ketan Kshirsagar, Jack Grinblatt, Jon Tao, Eliada Ziraj "
date: "4/11/2021"
output: 
  html_document:
    toc: true
    theme: readable
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Build Data Model

### Set up Libraries
```{r, results='hide'}
#For decision tree, C5.0 
library(C50)
#For CrossTable
library(gmodels)
#For confusionMatrix
library(caret)
#For KNN
library(class)
#For ANN
library(neuralnet)
library(e1071)
```
### Definitions

T1, Temperature in kitchen area, in Celsius
RH1, Humidity in kitchen area, in % T2, Temperature in living room area, in Celsius RH2, Humidity in living room area, in %
T3, Temperature in laundry room area
RH3, Humidity in laundry room area, in % T4, Temperature in office room, in Celsius RH4, Humidity in office room, in %
T5, Temperature in bathroom, in Celsius
RH5, Humidity in bathroom, in % T6, Temperature outside the building (north side), in Celsius RH6, Humidity outside the building (north side), in %
T7, Temperature in ironing room , in Celsius
RH7, Humidity in ironing room, in % T8, Temperature in teenager room 2, in Celsius RH8, Humidity in teenager room 2, in %
T9, Temperature in parents room, in Celsius
RH9, Humidity in parents room, in % To, Temperature outside (from Chievres weather station), in Celsius Pressure (from Chievres weather station), in mm Hg RHout, Humidity outside (from Chievres weather station), in %
Wind speed (from Chievres weather station), in m/s
Visibility (from Chievres weather station), in km
Tdewpoint (from Chievres weather station), °C
rv1, Random variable 1, nondimensional
rv2, Random variable 2, nondimensional

### Import and Clean data

```{r}
energydata <- read.csv("KAG_energydata_complete.csv")
energydata$date <- NULL
energydata$T1 <- ifelse(is.na(energydata$T1),mean(energydata$T1, na.rm =T),energydata$T1)
energydata$T2 <- ifelse(is.na(energydata$T2),mean(energydata$T2, na.rm =T),energydata$T2)
energydata$T3 <- ifelse(is.na(energydata$T3),mean(energydata$T3, na.rm =T),energydata$T3)
energydata$T4 <- ifelse(is.na(energydata$T4),mean(energydata$T4, na.rm =T),energydata$T4)
energydata$T5 <- ifelse(is.na(energydata$T5),mean(energydata$T5, na.rm =T),energydata$T5)
energydata$T6 <- ifelse(is.na(energydata$T6),mean(energydata$T6, na.rm =T),energydata$T6)
energydata$T7 <- ifelse(is.na(energydata$T7),mean(energydata$T7, na.rm =T),energydata$T7)
energydata$T8 <- ifelse(is.na(energydata$T8),mean(energydata$T8, na.rm =T),energydata$T8)
energydata$T9 <- ifelse(is.na(energydata$T9),mean(energydata$T9, na.rm =T),energydata$T9)

energydata$RH_1 <- ifelse(is.na(energydata$RH_1),mean(energydata$RH_1, na.rm =T),energydata$RH_1)
energydata$RH_2 <- ifelse(is.na(energydata$RH_2),mean(energydata$RH_2, na.rm =T),energydata$RH_2)
energydata$RH_3 <- ifelse(is.na(energydata$RH_3),mean(energydata$RH_3, na.rm =T),energydata$RH_3)
energydata$RH_4 <- ifelse(is.na(energydata$RH_4),mean(energydata$RH_4, na.rm =T),energydata$RH_4)
energydata$RH_5 <- ifelse(is.na(energydata$RH_5),mean(energydata$RH_5, na.rm =T),energydata$RH_5)
energydata$RH_6 <- ifelse(is.na(energydata$RH_6),mean(energydata$RH_6, na.rm =T),energydata$RH_6)
energydata$RH_7 <- ifelse(is.na(energydata$RH_7),mean(energydata$RH_7, na.rm =T),energydata$RH_7)
energydata$RH_8 <- ifelse(is.na(energydata$RH_8),mean(energydata$RH_8, na.rm =T),energydata$RH_8)
energydata$RH_9 <- ifelse(is.na(energydata$RH_9),mean(energydata$RH_9, na.rm =T),energydata$RH_9)

energydata$T_out <- ifelse(is.na(energydata$T_out),mean(energydata$T_out, na.rm =T),energydata$T_out)
energydata$Press_mm_hg <- ifelse(is.na(energydata$Press_mm_hg),mean(energydata$Press_mm_hg, na.rm =T),energydata$Press_mm_hg)
energydata$RH_out <- ifelse(is.na(energydata$RH_out),mean(energydata$RH_out, na.rm =T),energydata$RH_out)
energydata$Windspeed <- ifelse(is.na(energydata$Windspeed),mean(energydata$Windspeed, na.rm =T),energydata$Windspeed)
energydata$Visibility <- ifelse(is.na(energydata$Visibility),mean(energydata$Visibility, na.rm =T),energydata$Visibility)
energydata$Tdewpoint <- ifelse(is.na(energydata$Tdewpoint),mean(energydata$Tdewpoint, na.rm =T),energydata$Tdewpoint)
energydata$rv1 <- ifelse(is.na(energydata$rv1),mean(energydata$rv1, na.rm =T),energydata$rv1)
energydata$rv2 <- ifelse(is.na(energydata$rv2),mean(energydata$rv2, na.rm =T),energydata$rv2)

energydatam <- as.data.frame(model.matrix(~.-1,energydata))
str(energydata)
summary(energydata)

```
# Build Models

## Linear Regression Model
```{r}

```

### Linear Regression Model Confusion Matrix
```{r}

```


## Logistic Regression Model

```{r}
#logit<-glm(RH_out ~., data = energydatam)
#summary(logit)

#energydata_pred<-ifelse(predict(logit, energydatam, type = "response")>0.1,3,0)
#summary(energydata_pred)

```

### Logistic Regression Model Confusion Matrix
```{r}
#confusionMatrix(as.factor(energydata_pred),as.factor(energydata$RH_out),positive = "1")
```


## Decision Tree Model
```{r}

```

### Decision Tree Model Confusion Matrix
```{r}

```


## ANN Model
```{r}

```

### ANN Model Confusion Matrix
```{r}

```


## Stacked Model
```{r}

```


### Stacked Model Confusion Matrix

# Analysis & Conclusions

