---
title: "Energy AI"
author: "Ketan Kshirsagar, Jack Grinblatt, Jon Tao, Eliada Ziraj, Aksshath Soundarrarajan"
date: "4/11/2021"
output: 
  html_document:
    toc: true
    theme: readable
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Build Data Model

### Set up Libraries
```{r, results='hide'}
#For decision tree, C5.0 
library(C50)
#For CrossTable
library(gmodels)
#For confusionMatrix
library(caret)
#For KNN
library(class)
#For ANN
library(neuralnet)
library(e1071)
# For stepwise
library(MASS)
```
### Definitions

date time year-month-day hour:minute:second

Appliances, energy use in Wh

lights, energy use of light fixtures in the house in Wh

T1, Temperature in kitchen area, in Celsius

RH1, Humidity in kitchen area, in % 

T2, Temperature in living room area, in Celsius 

RH2, Humidity in living room area, in %

T3, Temperature in laundry room area

RH3, Humidity in laundry room area, in % 

T4, Temperature in office room, in Celsius 

RH4, Humidity in office room, in %

T5, Temperature in bathroom, in Celsius

RH5, Humidity in bathroom, in % 

T6, Temperature outside the building (north side), in Celsius 

RH6, Humidity outside the building (north side), in %

T7, Temperature in ironing room , in Celsius

RH7, Humidity in ironing room, in % 

T8, Temperature in teenager room 2, in Celsius 

RH8, Humidity in teenager room 2, in %

T9, Temperature in parents room, in Celsius

RH9, Humidity in parents room, in % 

To, Temperature outside (from Chievres weather station), in Celsius

Pressure (from Chievres weather station), in mm Hg 

RHout, Humidity outside (from Chievres weather station), in %

Wind speed (from Chievres weather station), in m/s

Visibility (from Chievres weather station), in km

Tdewpoint (from Chievres weather station), °C

rv1, Random variable 1, nondimensional

rv2, Random variable 2, nondimensional

### Import and Clean data

```{r, cache=TRUE}
energydata <- read.csv("KAG_energydata_complete.csv")
energydata$date <- NULL
energydata$lights <- NULL
energydata$rv1 <- NULL
energydata$rv2 <- NULL
energydata$Appliances <- as.numeric(energydata$Appliances)
energydata$T1 <- ifelse(is.na(energydata$T1),mean(energydata$T1, na.rm =T),energydata$T1)
energydata$T2 <- ifelse(is.na(energydata$T2),mean(energydata$T2, na.rm =T),energydata$T2)
energydata$T3 <- ifelse(is.na(energydata$T3),mean(energydata$T3, na.rm =T),energydata$T3)
energydata$T4 <- ifelse(is.na(energydata$T4),mean(energydata$T4, na.rm =T),energydata$T4)
energydata$T5 <- ifelse(is.na(energydata$T5),mean(energydata$T5, na.rm =T),energydata$T5)
energydata$T6 <- ifelse(is.na(energydata$T6),mean(energydata$T6, na.rm =T),energydata$T6)
energydata$T7 <- ifelse(is.na(energydata$T7),mean(energydata$T7, na.rm =T),energydata$T7)
energydata$T8 <- ifelse(is.na(energydata$T8),mean(energydata$T8, na.rm =T),energydata$T8)
energydata$T9 <- ifelse(is.na(energydata$T9),mean(energydata$T9, na.rm =T),energydata$T9)

energydata$RH_1 <- ifelse(is.na(energydata$RH_1),mean(energydata$RH_1, na.rm =T),energydata$RH_1)
energydata$RH_2 <- ifelse(is.na(energydata$RH_2),mean(energydata$RH_2, na.rm =T),energydata$RH_2)
energydata$RH_3 <- ifelse(is.na(energydata$RH_3),mean(energydata$RH_3, na.rm =T),energydata$RH_3)
energydata$RH_4 <- ifelse(is.na(energydata$RH_4),mean(energydata$RH_4, na.rm =T),energydata$RH_4)
energydata$RH_5 <- ifelse(is.na(energydata$RH_5),mean(energydata$RH_5, na.rm =T),energydata$RH_5)
energydata$RH_6 <- ifelse(is.na(energydata$RH_6),mean(energydata$RH_6, na.rm =T),energydata$RH_6)
energydata$RH_7 <- ifelse(is.na(energydata$RH_7),mean(energydata$RH_7, na.rm =T),energydata$RH_7)
energydata$RH_8 <- ifelse(is.na(energydata$RH_8),mean(energydata$RH_8, na.rm =T),energydata$RH_8)
energydata$RH_9 <- ifelse(is.na(energydata$RH_9),mean(energydata$RH_9, na.rm =T),energydata$RH_9)

energydata$T_out <- ifelse(is.na(energydata$T_out),mean(energydata$T_out, na.rm =T),energydata$T_out)
energydata$Press_mm_hg <- ifelse(is.na(energydata$Press_mm_hg),mean(energydata$Press_mm_hg, na.rm =T),energydata$Press_mm_hg)
energydata$RH_out <- ifelse(is.na(energydata$RH_out),mean(energydata$RH_out, na.rm =T),energydata$RH_out)
energydata$Windspeed <- ifelse(is.na(energydata$Windspeed),mean(energydata$Windspeed, na.rm =T),energydata$Windspeed)
energydata$Visibility <- ifelse(is.na(energydata$Visibility),mean(energydata$Visibility, na.rm =T),energydata$Visibility)
energydata$Tdewpoint <- ifelse(is.na(energydata$Tdewpoint),mean(energydata$Tdewpoint, na.rm =T),energydata$Tdewpoint)


str(energydata)
summary(energydata)

```
# Build Models

## Linear Regression Model
```{r, cache=TRUE}
linreg<-lm(Appliances ~., data = energydata)
step.model <- stepAIC(linreg, direction = "both", 
                      trace = FALSE)
summary(step.model)
```

## Decision Tree
```{r}
energy_dt <- energydata

energy_dt$Appliances <- as.factor(energydata$Appliances)

set.seed(12345)
test_dt <- sample(1:nrow(energy_dt), 3947)

energy_dt_test <- energy_dt[test_dt,]
energy_dt_train <- energy_dt[-test_dt,]

dt_model <- C5.0(Appliances ~ ., data = energy_dt_train)
summary(dt_model)
```


## KNN
```{r}

normalize <- function(x) { 
  return((x - min(x)) / (max(x) - min(x)))
}
energy_dt <- as.data.frame(lapply(energydata, normalize))

#energy_y <- energy_dt[,1]
#energy_x <- energy_dt[,-1]

energy_train <- energy_dt_train[,-1]
energy_test <- energy_dt_test[,-1]

energy_labels_train <- energy_dt_train[,1]
energy_labels_test <- energy_dt_test[,1]

energy_labels_train <- as.factor(energy_labels_train)


knnmodel <- knnreg(energy_train, unclass(energy_labels_train), k = 137)
predy <- predict(knnmodel, data.frame(energy_test))

postResample(pred=predy,obs=unclass(energy_labels_test))


mse = mean((unclass(energy_labels_test) - predy)^2)
mse
mae=caret::MAE(unclass(energy_labels_test),predy)
mae
rmse=caret::RMSE(unclass(energy_labels_test),predy)
rmse


print(data.frame(unclass(energy_labels_test), predy))

```


## ANN Model
```{r, cache=TRUE}
normalize <- function(x) { 
  return((x - min(x)) / (max(x) - min(x)))
}
energy_norm <- as.data.frame(lapply(energydata, normalize))


str(energy_norm)
summary(energy_norm$Appliances)


set.seed(12345)

testset <- sample(1:nrow(energy_norm), 3947)

energytest <- energy_norm[testset,]
energytrain <- energy_norm[-testset,]

#need to make more complex, additional hidden layers, increase stepmax
annmodel <- neuralnet(Appliances ~ ., data=energytrain, hidden = 1, stepmax = 1000000)
plot(annmodel)
```

### ANN Model Performance
```{r, cache=TRUE}
model_results <- compute(annmodel, energytest)
summary(model_results$net.result)
results <- data.frame(actual=energytest$Appliances,prediction=model_results$net.result)
results

postResample(model_results$net.result,energytest$Appliances)

predicted_Appliance <- model_results$net.result


```

# Analysis & Conclusions

## Workflow
The project provided us a greater understanding of the importance of the underlying data in creating the optimal output. As an example, this dataset used 'energy consumption' in watt hours as a dependent variable, but the creator of the dataset rounded the output into intervals of 10. This allowed us to treat the dependent variable as both a factor and a numeric variable to use different models. This obviously caused complexity in handling the data but at the end the models worked.

## Output
Based on our analysis, we found the ANN model to be the most accurate at predicting energy consumption for appliances. This makes sense given the underlying data (humidity and temp levels for different internal and external locations around a home). As opposed to Decision Tree, KNN, and Linear which all were far less accurate at predicting energy consumption.

## Implications 
Given the data, the model can be applied to optimizing grid reliability in the real world. One can deploy sensors to capture real time humidity and temp data in a home and use to predict Appliance energy consumption, thereby forecasting behind-the-meter volitility and extrapolate to grid-scale demand. This can allow for better generation forecasting, better demand response event planning, and even target households with poorer performing appliances for appliance rebate programs. 

--- NOTES ---
1. Friday 16: Make ANN more compled and Remove ANN Confusion Matrix (not applicable for continuous), replace with MSE/MAPE (Eliada)
2. Friday 16: Optimize KNN (#k) (Ketan)
3. Friday 16: Repair Decision Tree (Jon)
4. Saturday 17: Analysis (Jack)

