---
title: "Analysis of Prosper Borrower Rates & Default Risk"
author: "Eliada Deschamps, Jack Grinblatt, Jon Tao, Ketan Kshirsagar, Aksshath Soundarrarajan"
date: "3/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The objective of this analysis is to model factors that translate to borrower rate as well as the default risk. The outcome of this analysis will allow Prosper to adjust borrower rate methodology as well as identify arbritrage opportunities.

## Methodology
1. Import Data
2. Clense Data
3. Run Linear Model to Evaluate Borrower Rate Factors
4. Run Logistic Regression Model to Evaluate Default Risk Factors
5. Analysis & Conclusions

For each of these steps, the analysis will show the code in R so Prosper analysts can understand the underlying mechanics of the analysis. Final conclusions can be found at the end of the report.


## 1. Import Data

```{r}

listings <- read.csv("ProjectA_Listings2013.csv")

```


## 2. Clense Data
```{r}

listings$loan_status <- as.factor(listings$loan_status)
listings$prosper_rating <-as.factor(listings$prosper_rating)
listings$scorex <-as.factor(listings$scorex)
listings$income_range <-as.factor(listings$income_range)
listings$income_range_description <-as.factor(listings$income_range_description)
listings$employment_status_description <-as.factor(listings$employment_status_description)
listings$occupation <-as.factor(listings$occupation)
listings$borrower_state <-as.factor(listings$borrower_state)
listings$borrower_city <-as.factor(listings$borrower_city)
listings$loan_status_description <- as.factor(listings$loan_status_description)
listings$loan_origination_date <- as.factor(listings$loan_origination_date)
listings$first_recorded_credit_line <- as.factor(substr(listings$first_recorded_credit_line, nchar(listings$first_recorded_credit_line)-3, nchar(listings$first_recorded_credit_line)))
listings$income_verifiable <- as.factor(listings$income_verifiable)
listings$is_homeowner <- as.factor(listings$is_homeowner)

str(listings)
summary(listings)

```


## 3. Build Linear Model for Borrower Rate
Linear Regresion Model: Includes Only Variables with Significant Correlation
```{r}
model1 <-lm(borrower_rate ~ number_of_days + principal_balance + loan_status + amount_funded + listing_term + listing_monthly_payment + scorex + prosper_score + listing_category_id + stated_monthly_income + employment_status_description + occupation + lender_indicator + monthly_debt + current_delinquencies + first_recorded_credit_line + amount_delinquent + bankcard_utilization + total_open_revolving_accounts + real_estate_balance + was_delinquent_derog + delinquencies_over30_days + is_homeowner, data = listings)

summary(model1)
```



## 4. Run Logistic Regression Model for Default Risk
```{r}
lrmodel1 <- glm(delinquencies_over30_days ~ borrower_rate + number_of_days + principal_balance + loan_status + amount_funded + listing_term + listing_monthly_payment + scorex + prosper_score + listing_category_id + employment_status_description + occupation + lender_indicator + monthly_debt + current_delinquencies + bankcard_utilization + total_open_revolving_accounts + was_delinquent_derog + is_homeowner, data = listings)

summary(lrmodel1)

```

## 5. Analysis & Conclusions

### Factors that Matter Most to Borrower Rate
Based on the linear model above, we conclude that standard factors measuring the consumer's loan, employment, and past deliquencies are all weighted highest in determining borrower rate, specifically:

Loan Descriptors
- Loan Status
- Size of Monthly Payments

Employment Descriptors
- Employment Status
- Income
- Specific Occupations

Other
- Past Delinquencies

None of these are suprising as they all together tell a story of the risk of a particular candidate, and price the loan higher with a higher rate for those that are more risky (e.g. in volitile industries, low income, or have a history of defaulting).

### Factors that Matter Most to Default Risk
Based on the logistic regression model above, we conclude that the expectations of default risk are somewhat in line with the public narrative but can be better defined:

1. Bankcard Utilization is one of the highest default risk factors. This makes sense given a particular customer may overleverage themselves and no longer be able to meet all their credit lines, and therefore have to prioritize.

2. Listing Monthly Payment also plays into this story, as the payment size goes up a customer may have a higher change of defaulting as natural variability in life occurs. Smaller payments are easier to manage.

3. Specific occupations are more likely to default given volitile industries (e.g. government jobs which have variable funding, real estate which is highly market based etc.)

4. Homeowners are also more likely to default, this likely plays in with the first point suggesting that when variability in life occurs, customers need to prioritize payments and homes tend to get prioritized over other loans.

### Recommendations
Given these findings, we recommend the following:

1. Adjust the borrower rate methodology to take into account the factors that truly matter to default risk.

2. Use a KNN or ANN model to cluster and segment consumers based on default risk, and create new financial instruments to decrease default risk (e.g. flexible monthly payments)

3. Continue to measure consumer behavior in real time and proactively target high risk customers with messaging and programs to keep them engaged with the loan, as a default is a loss all around.